\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-11 manuscript/main.tex
code: get_xi_direct unified

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given a basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
	In practice, functional predictors are observed only at a finite set of time points rather than as complete curves. Rather than reconstructing infinite-dimensional object stated above via finite observations, we approximate each predictor using a finite-dimensional projection by truncating its basis expansion at a finite number $M$. This $M$ can be set to a sufficiently large value (e.g., 15 or 20) to capture a wide range of functional patterns. 
	Notably, it is unnecessary to fine-tune $M$, as a  penalization scheme introduced in Section \ref{sec: Regularization of PLS Components} regularizes each functional component to achieve the desired smoothness. We denote the projected predictors and coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}

@@

	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm. This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply solving a linear equation.
	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).

	The goal is to find a unit-norm direction $\xi \in \mathcal{H}$, whose functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, that maximizes the empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$.
	We denote the solution as
	\begin{equation}
		\hat{\xi} 
		= 
		(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}),
	\end{equation}
	where $\hat{\boldsymbol{\zeta}} \in \mathbb{R}^p$ is the scalar part, and each functional part $\hat{\xi}_j \in L^2([0,1])$ lies in $\operatorname{span}(b_1(t), \ldots, b_M(t))$ and is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

	Let $\hat{\mathbf{d}}_j := (\hat{d}_{j1}, \ldots, \hat{d}_{jM})^\top \in \mathbb{R}^M$ and $\mathbf{y} := (y_1, \ldots, y_n)^\top$. 
	Let $B \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions, with entries
	\[
	B_{m, m'} := \langle b_m, b_{m'} \rangle, \quad m, m' = 1, \ldots, M.
	\]
	We compute $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ as 
	\begin{equation*}
		\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		\Theta_j^\top \mathbf{y},
		\quad
		%%%%%%%%%%%%%%%%
		\hat{\boldsymbol{\zeta}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		Z^\top \mathbf{y}.
	\end{equation*}
These expressions represent matrix–vector multiplications normalized by a common factor. 
	The derivation of this formula is provided in Appendix~\ref{section:proof:Proposition:linear_system_unregularized}.
	Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

	%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Let 
	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
		Let $\xi \in \mathcal{H}$ be any unit-norm direction such that its $1$st through $K$th functional components lie in $\operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr)$, respectively.
		Then, the empirical covariance between the projected component $\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}$ and the response $Y$, approximated in terms of the basis, is given by
		\begin{equation*}
			\widehat{\textnormal{Cov}} \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
			:=
			\frac{1}{n} 
			\sum_{i=1}^n
			y_i
			\langle \widetilde{\mathbf{W}}_i, \xi \rangle_{\mathcal{H}}.
		\end{equation*}
		Then the PLS component direction 
		$	\hat{\xi}$ 
		computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y )$.
	\end{proposition}

	The proof of Proposition \ref{Proposition: generalized rayleigh quotient} is given in the Appendix \ref{section:proof:eigenproblem_derivation}.

	\begin{proposition} \label{Proposition:linear_system_unregularized}
		aaa
	\end{proposition}
	Proof of is provided in Appendix \ref{section:proof:Proposition:linear_system_unregularized}.
	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
	Although Proposition \ref{Proposition: generalized rayleigh quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions. Thus, in this section, we provide a modification of Proposition  \ref{Proposition: generalized rayleigh quotient} that yields regularized (smoothed) PLS components.

@@

	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$. Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition \ref{Proposition: generalized rayleigh quotient} when $\lambda_k=0$ for all $k$. On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$. In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).

@@

	\subsection{Proof of Proposition \ref{Proposition:linear_system_unregularized}}\label{section:proof:Proposition:linear_system_unregularized}

@@

	presented in Proposition \ref{Proposition:linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:

@@

	Define the Lagrangian:
	\[
	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) = f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
	\]
	The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin. Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points. Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
	Taking gradients of $\mathcal{L}$ and setting them to zero yields:
	\begin{align*}
		\nabla_{\mathbf{d}_j} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		B \Theta_j^\top \mathbf{y}
		- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
		\numberthis \label{lag_grad_d}
		\\
		\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		Z^\top \mathbf{y}
		- 2\lambda \boldsymbol{\zeta} = 0.
		\numberthis \label{lag_grad_zeta}
	\end{align*}
	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
	$$
	\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
	$$
	all scaled by the same factor. There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above. The global maximizer is therefore given by
	\begin{equation*}
		\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		\Theta_j^\top \mathbf{y},
		\quad
		%%%%%%%%%%%%%%%%
		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		Z^\top \mathbf{y},
	\end{equation*}
	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{Proposition:linear_system_unregularized}.

	\subsection{Proof of Propositions \ref{Proposition: generalized rayleigh quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
	%
	%
	\begin{align*}
		\widehat{\textnormal{Cov}} (
		\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y 
		) 
		&= 
		\frac{1}{n} \sum \limits_{i=1}^n 
		y_i
		\langle \widetilde{\mathbf{W}}_i, \xi \rangle_\mathcal{H} \\
		&= 
		\frac{1}{n} 
		\sum \limits_{i=1}^n
		y_i
		\langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
		+  
		\frac{1}{n} 
		\sum \limits_{i=1}^n  
		y_i
		\langle \mathbf{Z}_i, 
		\boldsymbol{\theta} 
		\rangle 
		\\
		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
	\end{align*}

>>>>

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given a basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
Since functional predictors are observed at finitely many discrete time points, we approximate them by truncating the expansion at $M$ terms, yielding a finite-dimensional projection. A moderately large $M$ (e.g., 15 or 20) suffices to capture rich functional variation, and no fine-tuning is needed, as our method controlls smoothness  via penalization (Section~\ref{sec: Regularization of PLS Components}). We denote the truncated space by
	\begin{equation}
		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
	\end{equation}
	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}

@@

	\subsubsection{Smoothed estimation of PLS components}\label{sec: pls component computation intermediate}
	Building on the basis function approximation from Section~\ref{sec: finite basis approximation}, we now introduce an intermediate strategy for implementing the first step of the PLS algorithm. This approach directly obtains a hybrid PLS component direction, sharing the same structure as the hybrid predictors presented in \eqref{eq: Hybrid functional model}, by simply doing matrix-vector multiplications

	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
	The goal is to find a unit-norm direction $\xi \in 
	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
	 defined as
	 		\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
	 	:=
	 	\biggl(
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	\biggr)^2
	 	.
	 \end{equation}
	We denote the maximizer as
	\begin{equation*}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})
:= \arg \max_{\xi \in (\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}} \widehat{\textnormal{Cov}}^2 \left( \langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y \right)
	\end{equation*}
%
	where each functional part $\hat{\xi}_j $  is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

	%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Let

	\begin{proposition}\label{proposition:generalized_rayleigh_quotient}
At the $l$-th iteration of the PLS algorithm, the unit-norm direction in $(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance \eqref{def:squared_empirical_cov} is the solution to the following generalized eigenvalue problem:
\begin{align}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top B^\ast \boldsymbol{\xi} = 1,
	\label{eq: Regularized generalized rayleigh quotient equation}
\end{align}
where
$$
V := \frac{1}{n^2} (B^\ast \Theta^\top \mathbf{y})(B^\ast \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
$$
where
$B^\ast := \operatorname{blkdiag}(B, \ldots, B, I_p)  \in  \mathbb{R}^{(MK+p) \times (MK+p)}$,
 $\Theta := (\Theta_1, \ldots, \Theta_K, Z) \in \mathbb{R}^{n \times (MK + p)}$,
$B \in \mathbb{R}^{M \times M}$ is the gram matrix  of the basis functions  with entries
$
B_{m, m'} := \langle b_m, b_{m'} \rangle = \int_0^1  b_m(t)  b_{m'}(t) dt
$
for $m, m' = 1, \ldots, M$.
\end{proposition}
Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:generalized_rayleigh_quotient_linear}
	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$ in Proposition \ref{proposition:generalized_rayleigh_quotient} as 
\begin{equation*}
	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\zeta}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Proofs of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{proposition:generalized_rayleigh_quotient_linear} are provided in Appendix~\ref{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}.
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
	Although Proposition \ref{proposition:generalized_rayleigh_quotient} provides an efficient and principled way to compute the PLS components $\xi$, their functional part $\psi=(\psi^{(1)}, \ldots, \psi^{(K)})$ may not be smooth, which can lead to overfitting and unstable predictions. Thus, in this section, we provide a modification of Proposition  \ref{proposition:generalized_rayleigh_quotient} that yields regularized (smoothed) PLS components.

@@

	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$. Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:generalized_rayleigh_quotient} when $\lambda_k=0$ for all $k$. On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$. In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).

@@

	\subsection{Proof of Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}}\label{section:proof:proposition:generalized_rayleigh_quotient_linear_system_unregularized}

@@

	presented in Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized} is equivalent to the following constrained optimization problem on the Euclidean space:

@@

	Define the Lagrangian:
	\[
	\mathcal{L}(\{\mathbf{d}_j\}, \boldsymbol{\zeta}, \lambda) = f(\{\mathbf{d}_j\}, \boldsymbol{\zeta}) - \lambda g(\{\mathbf{d}_j\}, \boldsymbol{\zeta}).
	\]
	The constraint function $g$ is continuously differentiable, and its gradient vanishes only at the origin. Since the origin is not feasible (the constraint requires norm 1), the gradient of $g$ is nonzero at all feasible points. Thus, the linear independence constraint qualification (LICQ) holds, ensuring that the KKT conditions are necessary for local maxima (see, for example, Theorem 5.3.1 in \citealt{bazaraaNonlinearProgrammingTheory2006}).
	Taking gradients of $\mathcal{L}$ and setting them to zero yields:
	\begin{align*}
		\nabla_{\mathbf{d}_j} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		B \Theta_j^\top \mathbf{y}
		- 2\lambda B \mathbf{d}_j = 0, \quad \forall j, 
		\numberthis \label{lag_grad_d}
		\\
		\nabla_{\boldsymbol{\zeta}} \mathcal{L} &= 
		\frac{2}{n^2} 
		\left(
		\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}
		\right)
		Z^\top \mathbf{y}
		- 2\lambda \boldsymbol{\zeta} = 0.
		\numberthis \label{lag_grad_zeta}
	\end{align*}
	By pre-multiplying equation \eqref{lag_grad_d} by $B^{-1}$ and observing that the scalar quantity $\sum_{\ell=1}^K \mathbf{y}^\top \Theta_\ell B \mathbf{d}_\ell + \mathbf{y}^\top Z \boldsymbol{\zeta}$ appears in both \eqref{lag_grad_d} and \eqref{lag_grad_zeta}, the gradient conditions together imply that any local optimum must be  scalar multiples of
	$$
	\Theta_1^\top \mathbf{y}, \ldots, \Theta_K^\top \mathbf{y}, Z^\top \mathbf{y},
	$$
	all scaled by the same factor. There exists only one set of vectors  that also satisfies the primal equality constraint, namely the normalized version of the vector set above. The global maximizer is therefore given by
	\begin{equation*}
		\mathbf{d}_j^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		\Theta_j^\top \mathbf{y},
		\quad
		%%%%%%%%%%%%%%%%
		\boldsymbol{\zeta}^\ast = \frac{1}{\sqrt{\sum_{j=1}^K 
				\mathbf{y}^\top
				\Theta_j
				B \Theta_j^\top \mathbf{y} 
				+ 
				\mathbf{y}^\top Z Z^\top \mathbf{y}}}
		Z^\top \mathbf{y},
	\end{equation*}
	which are the same as  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\zeta}}$. This completes the proof of  Proposition \ref{proposition:generalized_rayleigh_quotient_linear_system_unregularized}.

	\subsection{Proof of Propositions \ref{proposition:generalized_rayleigh_quotient} and \ref{Proposition: Regularized generalized rayleigh quotient} }\label{section:proof:eigenproblem_derivation}
	%
	%
	\begin{align*}
		\widehat{\textnormal{Cov}} (
		\langle \widetilde{\mathbf{W}}, \xi \rangle_{\mathcal{H}}, Y 
		) 
		&= 
		\frac{1}{n} \sum \limits_{i=1}^n 
		y_i
		\langle \widetilde{\mathbf{W}}_i, \xi \rangle_\mathcal{H} \\
		&= 
		\frac{1}{n} 
		\sum \limits_{i=1}^n
		y_i
		\langle \widetilde{X_i}, \psi \rangle_\mathcal{F}  
		+  
		\frac{1}{n} 
		\sum \limits_{i=1}^n  
		y_i
		\langle \mathbf{Z}_i, 
		\boldsymbol{\theta} 
		\rangle 
		\\
		&=  \frac{1}{n} \sum \limits_{i=1}^n  \left\{ \sum \limits_{k=1}^K \int_0^1 X_i(t_k) \psi^{(k)}(t_k) dt_k \right\} Y_i +  \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
		&=  \frac{1}{n} \sum \limits_{i=1}^n \left[ \sum \limits_{k=1}^K \int_0^1 \left\{\sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t) \right\} \left\{\sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t) \right\} dt_k \right] Y_i + \frac{1}{n} \sum \limits_{i=1}^n \mathbf{Z}_i^\top \boldsymbol{\theta} Y_i \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top \left[ \sum \limits_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \left\{ \int_0^1 \mathbf{b}^{(k)}(t_k) \mathbf{b}^{(k)}(t_k)^\top dt_k \right\} \mathbf{a}^{(k)} \right] + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C} J \mathbf{a}) + n^{-1}\widetilde{\mathbf{y}}^\top \mathbf{Z} \boldsymbol{\theta} \\
		&= n^{-1} \widetilde{\mathbf{y}}^\top (\widetilde{C}J\mathbf{a} + \mathbf{Z} \boldsymbol{\theta}).
	\end{align*}
